R Notebook for conducting Minimum Detectable Change (MDC) Analysis to design a monitoring strategy for the Upper Yaquina River TMDL Implementation Plan

### 2024-02-15 msc.Rmd
add commands to calculate MDCs for current number of samples and MDC for additional samples. Then printed them to screen using formating for comparisson

No I tried the function for station 12301, which had the largest MDC

@@

MDC <- calculateMDCWithAdditionalSamples(model_cur,additional_samples, 
                                         alpha = 0.05, power = 0.9)

print(paste("MDC for", initial_n + additional_samples, "total samples:", MDC))

>>>>

Now I tried the function for station 12301, which had the largest MDC

@@

MDC_cur <- calculateMDCWithAdditionalSamples(model_cur,0, 
                                         alpha = 0.05, power = 0.9)

MDC_add <- calculateMDCWithAdditionalSamples(model_cur,additional_samples, 
                                         alpha = 0.05, power = 0.9)

print(paste("MDC for", initial_n + additional_samples, "total samples:", 
            sprintf("%f6", MDC_add), " compared to ", sprintf("%f6", MDC_cur),
            " for ", initial_n, " initial samples"))
